Interest Flooding Attacks and countermeasures in Named Data Networking

### 2013-01-14 03-interest-flooding.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@903 df1a90cd-247b-4364-bdaf-287a704eb499
Small update on section 3
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@914 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Interest Flooding Attacks in NDN}
\label{sec:interest flooding}

@@

Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers, and are routed through the network based on their content name prefix. These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN. An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker bot should request an unpopular or non-existing content (e.g., content with a unique name, \emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.

>>>>

\section{Interest Flooding Attacks in NDN}
\label{sec:interest-flooding}

@@

Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers, and are routed through the network based on their content name prefix. These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN. An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}). 
%%% Alex %%% We have (almost) exactly the same sentence in the intro. I think here is kind of redundant, as it is obvious how we call the attack from the section title.  Also, we are referring to the term again in the last paragraph of the section.
% We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.

@@

To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker should request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}). In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network. Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.
